### 2022-04-27 sections/papers.tex
LPPL v1.3c
Update papers.tex

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.md

@@

\begin{benumerate}{7}

@@

\item{\small Cuevas, C. {\itshape et al.} ({\itshape forthcoming}). Public Service Motivation Among Chilean Public Employees. {\itshape Revista del CLAD Reforma y Democracia}, 80. {\footnotesize \scshape [in Spanish]}. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}}\vspace{1mm}

@@

\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A. (2015). Undersecretaries Rotation in Chile: An Exploration of the Second Government Line, 1990-2014. {\itshape Revista de Gesti\'on P\'ublica, IV}(2), 151--190. {\footnotesize \scshape [in Spanish]}. \\ {\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}} \vspace{1mm}\pagebreak

@@

\begin{benumerate}{12}
\item{\small Gonz\'alez-Bustamante, B., \& Luci, F. ({\itshape forthcoming}). Political Elites in Latin America: Socialisation, Trajectories, and Capitals. Introduction. {\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28. {\footnotesize \scshape [in Spanish]}. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}}\vspace{1mm}

>>>>

%% LaTeX Project Public License v1.3c
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.md

@@

\item{Fleming, T., González-Bustamante, B., \& Schleiter, P. (2022, {\itshape forthcoming}). Cabinet Reshuffles and Parliamentary No-Confidence Motions. {\itshape Government and Opposition}.}\vspace{1mm}

@@

\item{\small Cuevas, C. {\itshape et al.} (2021, {\itshape forthcoming}). Public Service Motivation Among Chilean Public Employees. {\itshape Revista del CLAD Reforma y Democracia}, 80. {\footnotesize \scshape [in Spanish]}. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}}\vspace{1mm}

@@

\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A. (2015). Undersecretaries Rotation in Chile: An Exploration of the Second Government Line, 1990-2014. {\itshape Revista de Gesti\'on P\'ublica, IV}(2), 151--190. {\footnotesize \scshape [in Spanish]}. \\ {\scshape doi}: \href{https://doi.org/10.22370/rgp.2015.4.2.2230}{\textcolor{blue}{10.22370/rgp.2015.4.2.2230}}} \vspace{1mm}

@@

\begin{benumerate}{12}
\item{\small Gonz\'alez-Bustamante, B., \& Luci, F. (2021, {\itshape forthcoming}). Political Elites in Latin America: Socialisation, Trajectories, and Capitals. Introduction. {\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28. {\footnotesize \scshape [in Spanish]}. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}}\vspace{1mm}
